---
params:
  chart_summary: NA #used
  snapshot_data: NA #used
  profile_summary: NA #used
  summary_data: NA
  comp_summary: NA
  geoname_summary: NA
  geotype_summary: NA
  geocomp_summary: NA
# geometry:  margin=0.5cm
output: html_vignette
  # pdf_document:
  #   includes:
  #     in_header: preamble.tex
  
  # To do,:
    # add column layout - still doesn't work in word. What if I create the charts in ggplot
    # then merge each column using ggpubr putting all in line and then merge the columns
    # will this respect the size 
    # what about a solution exporting all charts as png within the rmd and then using the images
    # in the report
    # add conditions to input$chart_summary
    # move to ggplot
    # figure out width of plots
    # if using html size is an issue
    
---
```{r setup}
knitr::opts_chunk$set(echo = F, cache = T)
```


```{r include=FALSE}
###############################################.
## Functions ----
###############################################.

  ###############################################.
  # Function that creates a snapshot plot for a domain
  plot_profile_snapshot <- function(domainchosen) {

    # only selecting decided domain
    prof_snap_data <- params$snapshot_data %>% subset(domain == domainchosen) %>%
      droplevels() %>%
      mutate(indicator = as.factor(indicator))

    #If no data available for that period then plot message saying data is missing
    if (is.data.frame(prof_snap_data) && nrow(prof_snap_data) == 0)
    {
      plot_nodata(height = 50)
    } else {

      # Tooltip
      if (params$comp_summary == 1) {#depending if time or area comparison
        tooltip_summary <-  c(paste0("Area: ", prof_snap_data$measure, " || ",
                                     "Comparator: ", prof_snap_data$comp_m, "<br>",
                                     prof_snap_data$trend_axis, "<br>", prof_snap_data$type_definition))
      } else if (params$comp_summary == 2) {
        tooltip_summary <-  c(paste0(prof_snap_data$trend_axis, ": ",
                                     prof_snap_data$measure, "  ||  ",
                                     "Baseline: ", prof_snap_data$comp_m, "<br>",
                                     prof_snap_data$type_definition))
      }

      # eliminating both axis
      axis_layout <- list(title = "", fixedrange=TRUE, zeroline = FALSE, showline = FALSE,
                          showticklabels = FALSE, showgrid = FALSE)


      # obtaining height for plot based on number of rows of indicators
      n_ind <- prof_snap_data %>% nrow()
      # when 0 or 1 indicators the plot needs at least that size to
      # prevent the spinner from showing and let the tooltip work
      height_plot <- case_when(n_ind > 1 ~ 38*n_ind+10,
                               TRUE ~ 75)

      # defining plot function
      plot_ly(prof_snap_data, y = ~indicator,   color = ~color, height = height_plot,
              colors=  c(blue = "#4da6ff", gray = "gray88", red = "#ffa64d", white = "#ffffff")
      ) %>%
        add_bars(x =1, showlegend= FALSE, width=1,
                 hoverinfo="text", hovertext = tooltip_summary,
                 marker = list(line= list(color="black", width = 0.5))) %>%
        # adding indicator name at center of each bar
        add_text(text = ~indic_multiline, x =0.5,  showlegend= FALSE,
                 textfont = list(color='black'), hoverinfo="skip" ) %>%
        layout(title = domainchosen,
               yaxis = axis_layout, xaxis = axis_layout,
               margin = list(b= 10 , t=5, l = 5, r = 0),
               font = list(family = '"Helvetica Neue", Helvetica, Arial, sans-serif')) %>% # to get hover compare mode as default
        config(displayModeBar = FALSE, displaylogo = F, editable =F)
    }
  }


```


#### `params$profile_summary` profile: `params$geoname_summary` 

```{r echo=FALSE}

    if (params$chart_summary == "Snapshot") {
      if (params$profile_summary == "HWB") {
        tagList(#Health and Wellbeing profile
          column(4,
                 plot_profile_snapshot("Behaviours"),
                 plot_profile_snapshot("Social care & housing"),
                 plot_profile_snapshot("Environment"),
                 plot_profile_snapshot("Life expectancy & mortality")
          ),
          column(4,
                 plot_profile_snapshot("Women's & children's health"),
                 plot_profile_snapshot("Immunisations & screening"),
                 plot_profile_snapshot("Economy"),
                 plot_profile_snapshot("Crime")
          ),
          column(4,
                 plot_profile_snapshot("Mental health"),
                 plot_profile_snapshot("Ill health & injury"),
                 plot_profile_snapshot("Education")
          )
        ) #taglist bracket
      } else if (params$profile_summary == "CYP") {
        tagList(#Children and young people profile
          column(4,
                 plot_profile_snapshot("Active"),
                 plot_profile_snapshot("Healthy")
          ),
          column(4,
                 plot_profile_snapshot("Included"),
                 plot_profile_snapshot("Nurtured"),
                 plot_profile_snapshot("Safe")
          ),
          column(4,
                 plot_profile_snapshot("Achieving"),
                 plot_profile_snapshot("Responsible")
          )
        )# taglist bracket
      }
    }
